{Hierarchy Builder:}\\ {Algebraic hierarchies} \\ {made easy} {in {\sc Coq} with {\sc Elpi}}

### 2020-07-01 talk-fscd/main.tex
colors for elpi code

\documentclass[11pt]{beamer}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{sourcesanspro}
\usepackage{sourcecodepro}
\usepackage{euler}
\usepackage[normalem]{ulem}
\usepackage{natbib}
\usepackage{apalike}

@@

  \begin{itemize}
  \item The predicate \L{from} stores an association between a factory
    \L{F}, a mixin \L{M} and the term \L{B} that can be used to build
    mixin \L{M} from factory \L{F}.
\begin{lstlisting}[language=Prolog, basicstyle=\footnotesize]
pred from o:factoryname, o:mixinname, o:term.
\end{lstlisting}
\vfill
  \item The predicate {\footnotesize\tt factory-requires} stores an
    association between a factory and a list of mixins that are
    pre-requisites to inhabiting this factory.
\begin{lstlisting}[language=Prolog, basicstyle=\footnotesize]
pred factory-requires o:factoryname, o:list mixinname.
\end{lstlisting}
    e.g. \L{group_of_monoid T} has the prerequisite that \L{T} is a
    monoid.
  \end{itemize}

>>>>

\documentclass[11pt]{beamer}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{sourcesanspro}
\usepackage{sourcecodepro}
\usepackage{euler}
\usepackage[normalem]{ulem}
\usepackage{natbib}
\usepackage{apalike}
\usepackage{minted} % pip3 install pygments, pdflatex -shell-escape hb
\newminted[elpicode]{../elpi.py:ElpiLexer -x}{linenos=false,fontsize=\footnotesize,frame=bottomline}

@@

  \begin{itemize}
  \item The predicate \L{from} stores an association between a factory
    \L{F}, a mixin \L{M} and the term \L{B} that can be used to build
    mixin \L{M} from factory \L{F}.
\begin{elpicode}
pred from o:factoryname, o:mixinname, o:term.
\end{elpicode}
\vfill
  \item The predicate {\footnotesize\tt factory-requires} stores an
    association between a factory and a list of mixins that are
    pre-requisites to inhabiting this factory.
\begin{elpicode}
pred factory-requires o:factoryname, o:list mixinname.
\end{elpicode}
    e.g. \L{group_of_monoid T} has the prerequisite that \L{T} is a
    monoid.
  \end{itemize}
